\documentclass[a4paper, 10pt]{article}

\usepackage{minted}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{syntax}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{hyperref}
\usepackage{libertine}
%\usepackage[T1]{fontenc}

\title{Channel Allocation in SC-FDMA: Research assignment}
\author{Noric Couderc}
\date{\today}

\begin{document}

\maketitle
\tableofcontents

\section{Background}

\subsection*{System model, problem definition and notation}
In order to test the current implementation of the algorithm, a reference
implementation is used. The reference implementation uses constraint programming
to find optimal solutions to the problem at hand. Therefore, the mathematical
model of a setup for \textbf{Min-Power} is hereby stated.

\subsubsection*{Parameters}

\begin{itemize}
    \item Set of users: $\mathcal{M} = \{1,\dots,M\}, M \in \mathbb{N}$.
    \item Set of channels: $\mathcal{N} = \{1,\dots,N\}, N \in \mathbb{N}$.
    \item Power limit function: $P^u = \mathcal{M} \rightarrow \mathbb{R}^+$.
    \item Channels peak power limit: $P^s = \mathcal{N} \rightarrow \mathbb{R}^+$.
    \itam Power function: $P_{uc} : \mathcal{M} \times \mathcal{N} \rightarrow \mathbb{R}$.
    % \item Utility value of assigning block $b$ to user $i$: $u_{ib} \in \mathbb{R}^+$.
    \item Demand target of user $i$: $d_i \in \mathbb{R}+$.
    \item The gain of user $i$ on channel $j$: $g_{ij} \in \mathbb{R}^+$.
    \item The channel bandwith: $B \in \mathbb{R}^+$.
    \item The noise power spectral density times the channel bandwidth:
    $\sigma \in \mathbb{R}^+$.
    \item The rate of user $i$, on channel $j$, with power $p_{j_i}$:
    $f(i,j,p_{j_i})
    \rightarrow \mathbb{R}^+$, where $p_{j_i}$ is the power consumed by user
    $i$ on channel $j$ (depends of the number of 
        channels assigned to $i$, defined below). 
\end{itemize}
\textbf{Note:}``user $i$" refers to $i \in \mathcal{M}$, ``channel $j$" refers to
$j \in \mathcal{N}$, ``block $b$" refers to $b \in \mathcal{B}$.

\subsubsection*{Variables}
\begin{itemize}
    \item Set of channel blocks: $\mathcal{B}$ where each element $b_i \in
    \mathcal{B}$ is itself a set of channels allocated to user $i$.
    \item Each user $i$, allocated $n$ channels will use, for each
          allocated channel $c$~: $p_{c_i} = \min\{ P^u / n, P^s\}$.
          
          Therefore, each user $i$, allocated a block $b_i$ will use:
          $p_{b_i} = |b_i| \min\{ P^u / |b_i|, P^s\}$.
\end{itemize}

\subsubsection*{Cost function}
The problem of \textbf{Min-Power} is to minimize:
\begin{align*}
     P &= \sum\limits_{i \in \mathcal{M}} p_{b_i}
 \end{align*}

\subsubsection*{Constraints}
\begin{itemize}
    \item Each user is allocated one block: $|\mathcal{B}| = |\mathcal{M}|$.
    \item All blocks contain channels: $\forall i \in \mathcal{M}: b_i \subseteq \mathcal{N}$.
    \item Each pair of user is allocated different channels.
    \begin{align*}
    \forall i,j \in \mathcal{M}: i \neq j \leftrightarrow b_i \cap b_j = \emptyset
    \end{align*}
    \item The block $b_i$ allocated to user $i$ should satisfy user $i$'s
    demand:
    \begin{align*}
        \forall i, b : \sum\limits_{j \in b}
        f(i, j, p_{j_i}) \geq d_i \text{where:}\\
        f(i, j, p_{j_i}) = B \log_2(1 + \frac{p_{j_i}g_{ij}}{\sigma^2})  
    \end{align*}
    \item For each user $i$, the power level $p_{b_i}$ is less than the users power limit. 
    \begin{equation*} 
        \forall i \in \mathcal{M} : p_{b_i} \leq P^u
    \end{equation*}
    \item The power level must stay under the channels peak power limit.
    \begin{equation*}
    \forall i \in \mathcal{M} : p_{b_i} \leq P^s
    \end{equation*}
\end{itemize}

\subsubsection*{Allocation Schemes}
The constraints on blocks change depending of the allocation scheme.
\begin{itemize}
    \item Localized: All blocks are convex sets (they contain only
            consecutive channels). 
    \begin{equation*}
    \forall b \in \mathcal{B}: 1 + \max(b) - \min(b) = |b|
    \end{equation*}
    \item Interleaved: All channels in a block are equally spaced. 
    That is, for each block $b \in \mathcal{B}$ its elements are spaced by a value $s$: 
    \begin{equation*}
        \forall c, c' \in b : c \neq c' \leftrightarrow |c' - c| = s
    \end{equation*}
    %For this particular constraint, we construct the set in several
    %steps. Given a spacing parameter $s$, the desired size $c$, and
    %the desired first channel $m$, each potential block $b$ is built:
    %\begin{enumerate}
    %    \item Build the set $b_1 =
    %    \{-\lfloor c/2 \rfloor,\cdots,\lfloor c/2 \rfloor\}$.
    %    \item Multiply all components of $b_1$ by the spacing parameter
    %    $s$. $\forall i \in b_1 : b_{2}(i) = s i$
    %    \item $\min b_3 = m$ : $\forall j \in b_2 : b_3(j) = \min(s_2) + m + j$
    %\end{enumerate}
\end{itemize}

\section{A variation of the algorithm: details}

\section{Algorithm description}

\section{Performance comparison}

\section{Results, discussion and analysis}

\section{Conclusion}

\bibliographystyle{ieeetr}
\bibliography{literature}

\end{document}
